\section{ChangLog}

From Memo $V2.1$ to Memo $V3.0$:
    According to Prof. Haibo Li's suggestion, we have optimised our analysis method and applied several new requirement to suppress the background. The details are listed as follow:
  \begin{itemize}
    \item Add the one-constraint kinematic fit on $\eta$ and $\piz$ for $\lambdacp\to p\eta(\gamma\gamma)$ and $\lambdacm \to p\piz$, and require the $\gamma\gamma$ invariant mass to be within $3\sigma$ of mass resolution, and require $\chi_{\rm{KF}}^2<$ 50 for $\piz$ and $\chi_{\rm{KF}}^2<$ 20 for $\eta$. Thus, the relevance correction for $\Delta E$ vs. $M(\gamma\gamma)$ has been cancelled.
    \item Add the further requirement on the $V_{\rm{r}}<0.2cm$ for (anti-)proton to suppress background (anti-)proton produced from the electron/positron beam or particles in final states interacting with the MDC inner wall or residual gas inside beam-pipe, especially for proton. The details are illustrated in Appendix~\ref{app:vrcut}.
    \item Add lateral moment and $E_{3\times3}/E_{5\times5}$ to distinguish photon showers in EMC with showers from other particles, especially for anti-neutron. we require lateral moment for shower shape to be less than 0.4, as well as $E_{3\times3}/E_{5\times5}$ to be larger than 0.85, where the $E_{3\times3}$ and $E_{5\times5}$ are the shower energy sum of $3\times3$ and $5\times5$ crystal around seed. The details are illustrated in Appendix~\ref{app:showercut}.
    \item Add a further requirement $|cos\theta_{\rm{decay}}|<0.9$ for $\eta\to\gamma\gamma$ to remove wrong combinations of photons for $\eta$ candidate, where $\theta_{\rm{decay}}$ is the polar angle of one photon in the $\eta$ rest frame. The detail study of $|cos\theta_{\rm{decay}}|$ distribution by data and MC samples is illustrated in Appendix~\ref{app:etaAngle}.
    \item For $\eta\to\pppm\piz$, apply $3\sigma$ of invariant mass resolution requirement.
  \end{itemize}
    We have updated the Memo with these new requirement, fitted results, systematic errors and I/O check. 