\section{Event Selection}
\label{ST-selection}
At $E_{cm} = 4.178 GeV$, pairs of $D_{s}D_{s}^{*}$ are produced,  and the $D_{s}^{*}$ decays to either $D_{s}\gamma$ or $D_{s}\pi^{0}$.  We use double tag method to select our signal events.


\subsection{Tracking, PID, $\pi^{0}/\eta^{(')}$ and $K_{S}^{0}$ Rconstruction }
$D_{s}$ candicates are built from $K^{\pm}$, $\pi^{\pm}$, $\pi^{0}/\eta^{(')}$ and $K_{S}^{0}$. The selections of the particles to build $D_{S}$ candicates are performed with DTagAlg-00-01-05 package with the default setting, which are summarized below.

\begin{itemize}
	\item Tracking:
		\begin{itemize}
			\item[-] The properties of charged tracks are determined based on the MDC information. Charged track candidates must satisfy:
				\begin{itemize}
					\item[-] $|cos\theta| < 0.93$.
					\item[-] $|dr| < \boldmath 1cm$ and $|dz| < \boldmath 10cm$,

						where $|dr|$ and $|dz|$ are defined as the one reconstructed minus the interaction point.
				\end{itemize}
		\end{itemize}
	\item Particle ID:
		\begin{itemize}
			\item[-] Charged tracks are identified as pion or kaon with Particle Identification (PID), which is implemented by combing the information of the energy loss (dE/dx) in MDC and the time-of-flight measured from
				the TOF system. Kaon and Pion are identified with the requirements that 
				\begin{itemize}
					\item[-] $\emph{Prob(K)} > 0$ and $\emph{Prob(K)} > \emph{Prob($\pi$)}$ for \emph{K},
					\item[-] $\emph{Prob($\pi$)} > 0$ and $\emph{Prob($\pi$)} > \emph{Prob(K)}$ for \emph{$\pi$},
						where \emph{Prob(X)} is the probability of hypothesis X, X can be \emph{$\pi$} or \emph{K}.
				\end{itemize}
		\end{itemize}
	\item $\pi^{0}/\eta$ selection: $\pi^{0}$ candidates are reconstructed through $\pi^{0} \rightarrow \gamma\gamma$ with package of PioEtaToGGRecAlg.
		

		The photons are reconstructed as energy showers on the EMC. We require:
		\begin{itemize}
			\item[-] Minimum energy for barrel showers( $|cos\theta| < 0.8$): $E_{min} >25MeV/c^{2}$,
			\item[-] Minimum energy for endcap showers( $0.86 < |cos\theta| < 0.92$): $E_{min} >50MeV/c^{2}$,
			\item[-] Shower within other $|cos\theta|$ regions are rejected.
			\item[-] EMC time requirements for events with at least one charged track detected: $0 \le t \ge 14 $(50ns),
		\end{itemize}

		Then we perform a constrained fit on the photon pairs to the nominal $\pi^{0}/\eta$ mass and require:
		\begin{itemize}
			\item[-] The unconstrained invariant mass for $\pi^{0}$: $0.115 < M(\gamma\gamma) < 0.015 GeV/c^{2}$,
			\item[-] The unconstrained invariant mass for $\eta: 0.490 < M(\eta) < 0.580 GeV/c^{2}$,
			\item[-] Mass fit: $\chi_{1c}^{2} < 30$.
		\end{itemize}
	\item $\eta^{'}$ selection: The $\eta^{'}$ candidates are reconstructed with $\pi^{+}\pi^{-}\eta$, the invariant mass for $\pi^{+}\pi^{-}\eta$ is required to fall into the range of $[0.938, 0.978] GeV^{2}$.
	\item $K_{S}^{0}$ selection: $K_{S}^{0}$ candidates are reconstructed using VeeVertexAlg package with two opposite charged tracks with requiring:
		\begin{itemize}
			\item[-] $|cos\theta| < 0.93$
			\item[-] $|dz| < 20 \emph{cm} $
		\end{itemize}

		For each pair of tracks, a constrained vertex fit is performed and the track parameters' results are used to get the invariant mass $M(K_{S}^{0})$. Then the decay length of $K_{S}^{0}$ is obtained with second vertex 
		fit by the SecondVertexFit package. For $K_{S}^{0}$ selection, we require:
		\begin{itemize}
			\item[-] $0.487GeV/c^{2} < M(K_S^{0}) < 0.511 GeV/c^{2}$.
			\item[-] Significance of the $K_{S}^{0}$ decay lenght has two standard deviations.
		\end{itemize}

	\item $D_{s}$ selection: According to the MC study on $D_{s}$ reconstruction (BESS\uppercase\expandafter{\romannumeral3}-DocDB-380), the $D_{s}$ candidates fall into the mass window of $1.90 < m_{D_{s}} < 2.03 GeV/c^{2}$ and 
		the corresponding $M_{rec}$ satisfied $2.051 < M_{rec} < 2.180 GeV/c^{2}$ are retained for further study. In which, the definition of $M_{rec}$ is
		\begin{equation}
			M_{rec} = \sqrt{(E_{cm} - \sqrt{p_{D_{s}}^{2} + m_{D_{s}}^{2})^{2}} - |\vec p_{cm} - \vec p_{D_{s}} | ^{2}} \; , \label{con:inventoryflow}
		\end{equation}
		where $E_{cm}$ is the energy of initial state, calculated from the beam energy ~\cite{DocDB 580-v1}, $\vec p_{D_{s}}$ is the momentum of $D_{s}$ candidate, $m_{D_{s}}$ is $D_{s}$ mass quoted from PDG ~\cite{PDG} and $\vec p_{cm}$ and $\vec p_{D_{s}}$ are four-momentum of initial state and the decay products of a $D_{s}$ candidate, respectively.
\end{itemize}

\subsection{Sigal Selection}
\par{


    We use different methods to select events in model indepent analysis(Sec. \ref{MIPWASelection}), amplitude analysis(Sec. \ref{AASelection}) and branching fraction measurement(Sec. \ref{BFSelection}).
And the details are in the correspongding sections.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%
